\SetPicSubDir{ch4-Results}

\subsection{ch4-Results}

This research is poised to deliver significant contributions to both academic and industrial practice by addressing critical, unresolved challenges in the real-world implementation of Occupant-Centric Control (OCC).
By moving beyond the conventional assumption of static occupancy and tackling the operational burden of comfort modeling, this study offers a novel, validated framework with far-reaching implications. 
The specific contributions are detailed below.

\section{Contributions to Academia}

\begin{itemize}
    \item It systematically quantifies the impact of dynamic occupancy patterns (e.g., variability, turnover) on the performance of different OCC strategies, addressing a critical gap left by prior studies that have largely assumed static occupancy.
    \item It provides a novel, empirically-validated operational framework for maintaining comfort models with minimal survey effort in live, multi-occupant settings. This moves beyond theoretical proposals by demonstrating a practical solution to the critical barrier of survey fatigue.
    % \item It introduces a robust methodology for evaluating OCC performance in realistic scenarios, bridging the gap between simplified simulations and complex real-world building dynamics.
\end{itemize}

\section{Contributions to Industry}
\begin{itemize}
    \item It delivers actionable guidance for facility managers to make data-driven, high-ROI decisions on where to deploy advanced OCC, targeting specific zones based on their occupancy patterns rather than relying on a costly building-wide approach.
    \item It offers a cost-effective and scalable framework that directly addresses industry concerns over the high operational cost and occupant disruption of frequent surveys, making advanced OCC more economically viable for widespread adoption.
    \item The proposed solution enhances building asset value by better supporting modern flexible work styles (e.g., Activity-Based Working) and contributes to the dual goals of energy efficiency and occupant well-being.
\end{itemize}