\SetPicSubDir{ch5-Discussion}

\subsection{Effect of occupancy parameters to comfort achievement}

In terms of previous studies, \cite{jung_energy_2020} investigated the effect of room-occupant amount to the performance of adopting member-oriented comfort models.
The difference is that study by \cite{jung_energy_2020} focused on the effect of occupancy amount, which accounts of static group comfort models in our studies.
In Figure~\ref{fig:ComfAgentic}\subref{fig:ComfImp}, it is shown that as room-member size increases around 5 to 6, the benefit of using static comfort models diminishes to nearly equal to baseline control(24 degree).
In \cite{jung_energy_2020} the relation of number of human agents and the performance of using group comfort models was simulated with different methods of deciding temperature setpoint using comfort models.
In their study, improvemnent of thermal comfort converge to nearly two percent as the number of human agents increases to 6, which is similar to our results in Figure~\ref{fig:ComfAgentic}\subref{fig:ComfImp}. 


The results indicates that the benefit of introduces real-time conrol models remain over 10\% in comparison with baseline(same temperature to be 24 degree) control in rooms with relatively larger number of users.

However, the benefit of using such control models are affected by various components such as sparcety of occupancy as shown in Figure \ref{fig:}, and occupancy dynamics such show in \autoref{}.

\subsection{Effect of occupancy parameters to control}

As examined in \autoref{subsec:controleffect}, in the wide range of sub-group size and occupancy condition, adjustment range is over \qty{1.0}{\celsius}.
Even at the large size of k and higher size of mean occupancy, the adjustment range is over \qty{0.5}{\celsius}.
The results indicate that the required temperature adjustment range used in \ac{rtgcm} control would large compared to the thermostat control, which is commonly \qty{0.5}{\celsius}.
As shown in \autoref{subsec:ComfPerf} the benefit of comfort performance of \ac{rtgcm} control from the baseline control remains at the large size of sub-group approximately \qty{10}{\percent}.
In this simulation, it is assumed that control temperature can be adjusted with the resolution of \qty{0.1}{\celsius}.

In control nature, it means that as the resolution of adjustable temperature is sufficiently high, the achievable comfort performance would be also higher.
This indicate introducing \ac{rtgcm}-based control would be able to achieve better comfort performance than \ac{sgcm} or \ac{dgcm} in more higher-resolution control system, even at common control adjustment step \qty{0.5}{\celsius}.

As examined in \autoref{fig:CtrlWindowRatio}, \ac{utr} has strong effect to the probability of required temperature adjustment.
Also in \autoref{fig:UTRexamples}, the different trend is observed between shared office and seat-assigned office such as KD.
As observed, the shared-offices marks dynamic range of \ac{utr}, while offices generally marks lower values such as 0.2 to 0.4.
From these analysises, it is indicated that shared-type offices may have more opportunities compared to standard offices.
Also some offices have specific weekly pattern of \ac{utr} as observed, in the KD and shared office 2.
In actual operation, these offices have group meetings outside the target office rooms on Monday afternoon.
\ac{utr} is able to follow such office dunamic usage pattern, indicating the effectiveness of using \ac{rtgcm} at such offices.